DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-05 ase2017/paper.tex
changed title of our tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
added comments in the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

A graphical user interface application was developed (Fig.~\ref{fig:gui-for-tf}) 
to favor digital controller synthesis in MATLAB, besides improving usability and, 
consequently, attracting more digital dynamical system engineers. Users can provide all 
required parameters for digital controller synthesis: physical plant specification, 
fixed-point representation and dynamic inputs. 
%
\begin{figure}
  \includegraphics[width=0.5\textwidth]{screens_dssynth.png}
  \caption{GUI application for the digital controller synthesis based on the transfer function representation.}
  \label{fig:gui-for-tf}
\end{figure}

>>>>

A graphical user interface application was developed (Fig.~\ref{fig:gui-for-tf}) 
to favor digital controller synthesis in MATLAB, besides improving usability and, 
consequently, attracting more digital dynamical system engineers. Users can provide all 
required parameters for digital controller synthesis: physical plant specification, 
fixed-point representation and dynamic inputs. 
%
\begin{figure}
  \includegraphics[width=0.5\textwidth]{screens_dssynth.png}
  \caption{GUI application for the digital synthesis based on the transfer function representation. \textcolor{red}{Lennon, can you please split this figure into 4 subfigures? The idea is to assign a label for each subfigure to explain a given step of our synthesis process}
}
  \label{fig:gui-for-tf}
\end{figure}
